### 2021-03-16 input/experiments.tex
small changes
wip
scoped broadcst section

@@

@@

>>>>

We also propose an implementation that further decreases generated
traffic and improves on anonymity~\cite{whitaker2002forwarding}.
\NAME makes extensive use of paths to enable deleting messages without
incrementing local counters. Messages carry their respective path and
processes detect when such messages have been looping when they carry
their identity (see Lines~\ref{line:notloopingA} and
\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
membership is all that matters, we propose to trade vectors of
identities for Bloom filters~\cite{almeida2007scalable}. Processes
know with high probability if they already received and forwarded each
message without knowing the identity of all processes that received
it.  False positive probability only incurs premature stopping of
broadcast messages and does not invalidate the delete of specific
messages.

@@

Compare with full broadcast full replication; timeout on removals.

Confirm complexity analysis.

@@

\subsection{\TODO{Extension: $A^4$?}}

### 2021-03-16 input/proposal.tex
scoped broadcst section

In this paper, we propose to dynamically adapt the scope of
S-broadcast using S-broadcast itself.  At any time, a process can
become the source of a new logical partition by transitively modifying
the respective state of neighboring processes using path weights.
When a process S-broadcasts a message in this partition, it reaches
all processes belonging to this partition. While the first partition
gathers all processes of the system, the following partitions reduce
the membership size of their neighboring partitions. In turns, the
traffic generated to adapt scopes scales with the number of
partitions.

\begin{definition}[Consistent partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source process.  $\forall p \in
  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

@@

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when weights are scalar values, and
processes only add new partitions to the system.  At any time, a
process running this protocol can add a logical partition to its
distributed system.  Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition by S-broadcasting their
respective \underline{a}dd message: $\alpha_a^0$ and
$\alpha_c^0$. They initialize their own state with the lowest possible
bound $0$ (see Line~\ref{line:lowestbound}), and send a message to
each of their neighbors by accumulating the corresponding edge weight
(see Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process
$b$ receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition.  In Figure~\ref{fig:addD}, processes discard last
transiting messages. The system converged to the optimal partitioning.
Transitive relationships ensure that each process gets its closest
source while accumulation of weights ensures that messages propagation
terminates.

@@

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity.

@@

\paragraph{A last optimization.}
\NAME makes extensive use of paths to enable deleting messages without
incrementing local counters. Messages carry their respective path and
processes detect when such messages have been looping when they carry
their identity (see Lines~\ref{line:notloopingA} and
\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
membership is all that matters, we propose to trade vectors of
identities for Bloom filters~\cite{almeida2007scalable} to improve on
generated traffic and
anonymity~\cite{whitaker2002forwarding}. Processes know with high
probability if they already received and forwarded each message
without knowing the identity of all processes that received it.  False
positive probability only incurs premature stopping of broadcast
messages and does not invalidate the delete of specific messages.

>>>>

In this paper, we propose to dynamically adapt the scope of
S-broadcast using S-broadcast itself. At any time, a process can
become the source of a new logical partition by transitively modifying
the respective state of neighboring processes using path weights. When
a process S-broadcasts a message in this partition, it eventually
reaches all processes belonging to this partition.  While the first
partition gathers all processes of the system, the following
partitions reduce the membership size of their neighboring
partitions. In turns, the traffic generated to adapt scopes scales
with the number of partitions.

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the only consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

%% \begin{theorem}[$SPED \implies CP$]
%%   \underline{S}hortest \underline{p}ath \underline{e}ventual
%%   \underline{d}elivery (SPED) where each process $k_n$ in the shortest
%%   path $\Pi_{ps}: [s, k_1,\ldots,k_n,p]$ eventually deliver the
%%   message forwarded by its predecessor $k_{n-1}$ leads to consistent
%%   partitioning.
%% \end{theorem}

%% \TODO{or:}

\begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
  Every process eventually delivers, hence forwards, the notification
  message $\alpha_s$ of its best partition $P_s$, eventually leading
  to consistent partitioning.
\end{theorem}

\begin{proof} When a process $s_1$ becomes a source, it belongs to
its own partition, for there exists no better partition than its own:
$\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It broadcasts such
message to its neighbors. Since communication channels are reliable,
neighboring processes eventually receive such notification. In
particular, whatever the order of received messages, every process
$p_1$ such that there exists no better partition $s_2$ than the
received one delivers and forwards it: $\forall s_2 \in S: |\Pi_{p
  s_1}| < |\Pi_{p s_2}|$. The notification emanating from $s_1$
transitively reaches all such processes through shortest paths. Since
there exists only one best value per process that can never be
retracted, processes eventually reach consistent partitioning.
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when
\begin{inparaenum}[(i)]
\item processes only have local knowledge about their direct
  neighborhoods,
\item weights are scalar values,
\item and processes only add new partitions to the system.
\end{inparaenum}
At any time, a process running this protocol can add a logical
partition to its distributed system.  Figure~\ref{fig:add} illustrates
its behavior on a system comprising 4 processes $a$, $b$, $c$, and
$d$. Two processes $a$ and $c$ concurrently create a partition by
S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
and $\alpha_c^0$. They initialize their own state with the lowest
possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
message to each of their neighbors by accumulating the corresponding
edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
not improve its partition distance. Processes $c$ and $d$ will never
hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
discard last transiting messages. The system converged to the
consistent partitioning. However, since processes operate using local
knowledge only, generated traffic may be sub-optimal, for processes
may receive, deliver, and forward messages emanating from a same
source simply because it did not come from the shortest path yet.

%% Transitive relationships ensure that each
%% process gets its closest source while accumulation of weights ensures
%% that messages propagation terminates.

@@

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity:
messages of old partitions may stop the notification of best sources,
for former weights are better than the newly received one.

@@
